Multi-modality Imagery Database for Plant Phenotyping

### 2015-07-22 response/response.tex

% Reviewer 1: Q14
\begin{review}
The conclusions (Sec. $6$) should be expanded.
\end{review}

\begin{response}
\todo{will expand after everything finished}
\end{response}

% Reviewer 1: Q15
\begin{review}
The acronym "MSU-PID" should be clearly defined when it first appears in text (p. $2$, line $51$)
\end{review}

\begin{response}
Except in the Abstract, the "MSU-PID" first appears in paragraph $4$ of Sec. $1$.
We have clearly defined it as short for Michigan State University Plant Image Database.
\end{response}

@@

% Reviewer 2: Q22
\begin{review}
The authors do a nice work of calibrating the cameras and measuring noise in the depth camera.
However, in page $2$ introduction says that this calibration allows for the explicit correspondence between pixels of any modality.
The authors rely on this to annotate data in one modality and propagate labels in the other (at least this is what I understand from later on description of methodology).
However, this is a VERY strong assumption and depends completely on the distance between the cameras, the angles, the distance between object and sensors and the actual object arrangement.
From our experience even when imaging co-planar plants (such as young Arabidopsis) at a distance of $\sim 70$cm even when the camera sensors are really close to each other (less than $5$cm) some differences in view are there and occlusions are present.
The authors should comment on this and should show as supportive evidence examples of plants at different growth stages in all $4$ modalities in raw and annotated form to show how close this correspondence is matching and how the propagated labels.
Furthermore, additional supporting evidence could be obtained either by arranging for two external and blind annotators to label some data (different age, different placement in the tray to show the effect of angle) in another modality (e.g., optical) and then measure inter-observer variability.
Then they can propagate annotations from fluorescence to images of that modality and measure agreement.
If this agreement is better than the in between rater variability then you could argue that propagating annotations is ok to do and actually beneficial.
Nevertheless, you should definitely mention this limitation of your work.
\end{review}

\begin{response}
\todo{Saif and Xi will work on the label transformation and edit the paper. }
\end{response}

@@

% Reviewer 2: Q23
\begin{review}
Furthermore, it assumes that cameras are perfectly synchronized which i) is not mentioned and ii) it cannot be done for some modalities since the same camera (with different filter) is used so some delay is expected.
Granted the plants may not move in between but this should be clarified and mentioned.
\end{review}

\begin{response}
We have this clarification in the paper. 
In Sec. $3.2.3$, we describes our image collection process, where the capture of all four modalities takes $4$ minutes. 
During this short period, no substantial movement or growth were observed. 
\end{response}

### 2015-07-22 datapapr_labeling.tex
Added label propagation figure.

>>>>

\begin{figure*}
\begin{centering}
\begin{tabular}{cccc}
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_ir.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_3_hour_23-seg_depth.png}\\
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_ir.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_5_hour_23-seg_depth.png}\\
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_ir.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_fmp.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_rgb.png}&
\includegraphics[width=.18\textwidth]{Figures/LabelAlignment/day_9_hour_20-seg_depth.png}\\
($a$) & ($b$) & ($c$) & ($d$) \\
\end{tabular}
\caption{Label propagation between all four modalities ($a$) infra-red, ($b$) fluorescence, ($c$) color and ($d$) depth, of a sample plant in the Arabidopsis collection for day 3 (top row), day 5 (middle row), and day 9 (bottom row).  In the dataset the manual segmentation is performed on the fluorescence images and is outlined here as orange lines propagated to all modalities.  The infra-red image is taken by the same camera and so will have close to exact pixel correspondence.  To assess the segmented pixel propagation to other modalities, we also manually labeled a subset of the color plant images and propagated this segmentation to all modalities (shown in cyan).  Comparing these boundaries in each modality gives a measure of the propagation errors due to parallax, and we provide quantitative analysis in table XXX.  Note that the color and depth images are rotated 90 degrees.}
\label{fig:LabelAlignment}
\end{centering}
\end{figure*}
